% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{paralist}
% Set your name here
\def\name{Dr Amit K Awasthi}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
%\def\footerlink{http://jblevins.org/projects/cv-template/}
\def \footerlink{~}
% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = magenta,
  pdfauthor = {\name},
  pdfkeywords = {Mathematics, Amit K Awasthi},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}
				
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.55\linewidth}
Assistant Professor\\
Department of Applied Mathematics \\
School of Vocational Studies and Applied Sciences\\
  \href{http://www.gbu.ac.in/}{\textbf{Gautam Budh University}},	Greater Noida \\
Gautam Budh Nagar- 201310\\
Uttar Pradesh, INDIA
\end{minipage}
\begin{minipage}{0.40\linewidth}
  \begin{tabular}{ll}
	Office: & +91 120 234 4357 \\
	Home: & +91 120 234 6319 \\
    Mobile: & +91 9650366665 \\
    %Fax: &  (919) 962-5678 \\
    Email: & \href{mailto:amitkawasthi@gbu.ac.in}{\tt amitkawasthi@gbu.ac.in} \\
		 & \href{mailto:awasthi.amitk@gmail.com}{\tt awasthi.amitk@gmail.com} \\
    %Homepage: & \href{http://www./}{\tt Web Link} \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
  \item B. Sc., MJP Rohilkhand University, 1997.

  \item M. Sc., MJP Rohilkhand University, 1999. [Gold Medal (University Topper)]

  \item Ph.D. Mathematics, Dr BR Ambedkar University, 2007.
	      \begin{itemize}
        \item Thesis Topic: \emph{A study of some delegated digital signature schemes.}
        %\item Thesis Proposal: \emph{Cooperative Task Processing}
        %\item Candidacy: \emph{Research  Problems in Distributed Control for Energy Systems}
        %\item Adviser: \href{#}{Professor Sundar Lal}
				\item Adviser: Professor Sundar Lal
        \item Area of Study: Cryptography
        \end{itemize}
\end{itemize}


\section*{Employment}

\begin{itemize}
\item Gautam Budh University,	Greater Noida  21/07/2011 -- Till Date.
\item PSIT Kanpur 01/08/2005 -- 19/07/2011.
\item HCST Mathura 20/11/2001	-- 29/07/2005.
\item TMIMT-Moradabad 22/08/2001 -- 19/11/2001
\item CES-Moradabad	06/08/2000 -- 21/08/2001.
\item SSPG College Shahjahanpur 01/09/1999 --	28/02/2000
\end{itemize}

\section*{Administrative Responsibilities}
\subsection*{Gautam Budh University}
\begin{itemize}
\item Coordinator, Examination, School of Voc. Studies and Applied Sciences [PRESENT]
\item Member, Web Committee [PRESENT]
\item Member, Department Web Committee, School of Voc. Studies and Applied Sciences  [PRESENT]
\item Warden, Sri Narayan Guru Hostel, Gautam Budh University [PRESENT]
\item Deputy Coordinator, Admission Office 
\item Member Syllabus Committee, School of Voc. Studies and Applied Sciences 

\end{itemize}

\subsection*{PSIT (Aff. Gautam Budh Technical University)}
\begin{itemize}
\item Dean Academics
\item Head, Department of Applied Sciences
\item Center Coordinator Examination Evaluation (MBA - GBTU)
\item In Charge System Management, Networking \& Soft Ware cell
\item Convener Ignitia (Tech Fest)
\end{itemize}

\subsection*{HCST (Aff. Gautam Budh Technical University)}
\begin{itemize}
\item Warden, Jr Hostel
\item Editor, College newsletter
\item Member, Lecture notes committee
\item Observer Examination (GBTU)
\end{itemize}

\section*{Medal/Awards etc.}
  \begin{itemize}
\item Gold Medal MERIT CERTIFICAT (M. Sc. Math)  By MJPR University Bareilly (For merit in University)
\item Gold Medal BAREILLY COLLEGE BAREILLY (M. Sc. Math) By Bareilly College Bareilly (For merit in M.Sc. prev. \& M.Sc. final)
\item Gold Medal SRI MEVARAM MEMOREAL   (M. Sc. Math)      By Bareilly College Bareilly (Other two Gold medal in Intermediate)
\item Consolation Prize for Elocution, Dept of Mathematics     Bareilly College Bareilly
\item Scholarship of Higher education Department, UP Government, LUCKNOW (1998-99) for M. Sc
\item Certificate for the most cited international research paper, (ESI)http://isiknowledge.com
\item Certificate: Significant contribution to the scientific community, By Elsevier Publishing   (New York) 
\item Certificate of Completion: Microsoft Digital Literacy Test - 05/06/2011    (www.Microsoft.com)

\item Institute excellence Award: [2005-2006], [2006-2007] (Gold Coin), [2007-2008] (Rs.15000/-), [2008-2009] ( Rs.15000/-), [2009-2010] (Certificate of Merit), [2010-2011] - PSIT Kanpur (GBTU)
\item A Laptop awarded for developing Online College system \& Academic performance (2005-2006) 
      PSIT Kanpur
\end{itemize}

\section*{Research Interests}
Cryptology, Network security, Digital Signatures, Smartcards, Authentication

\section*{Publications}
\subsection*{Books}
\begin{itemize}
\item Engineering Mathematics, (UG) \emph{Darbose, Prentice Hall}, (Co-authored with Dr. Sanjay Chaudhary), 2009
\end{itemize}

\subsection*{Journal Articles}

\begin{itemize}
\item Awasthi, A. K. and Lal, S., Proxy blind signature scheme, (Revised), \emph{Transaction 
               on Cryptology}, Vol. 2, Issue:  1, pp. 5 - 11 (2005).
\item Awasthi, A. K. and Lal, S., A new remote user authentication scheme with 
              forward secrecy,  \emph{IEEE Transactions on Consumer Electronics}, Vol. 49,  Issue: 4, 
              pp. 1246- 1248 (2003)
\item Awasthi, A. K. and Lal, S., An enhanced remote user authentication scheme, 
              \emph{IEEE Transactions on Consumer Electronics}, Vol. 50,  Issue: 2.Pp. 583- 586 (2004)
\item Awasthi, A. K., On the Authentication of the user from the Remote Autonomous 
              Object, \emph{International Journal of Network Security}, Vol.: 1, No: 3, pp. 166-167 
             (2005) 
\item Awasthi, A. K. and Lal, S., ID-based ring signature and proxy ring signature 
              schemes from bilinear pairings, \emph{International Journal of Network Security}, Vol. 4, 
               No: 2, pp. 187-192 (2007)

\item Awasthi, A. K., Remark on the Security of Strong Proxy Signature Scheme with 
               Proxy Signer Privacy Protection, \emph{IJICS}, Vol. 4, Issue 1 (2010)
\item Awasthi  A.  K. and  Srivastava  K. , An Improved Biometric Remote User 
              authentication Scheme Based On Nonce.  \emph{IJCNS}, 91, Vol. 2, No. 1  January (2010)
\item Awasthi A. K., An improved remote user authentication scheme with smartcards 
               using bilinear pairings, \emph{IJICS}, Accepted (2010).
\item	Awasthi A.K. and Srivastava K., R. C. Mittal, An improved timestamp-based  remote user authentication scheme, \emph{Computers and Electrical Engineering} 37 (2011), 869 -874                                                                                                  
\end{itemize}

\subsection*{Online Publication}

\begin{itemize}
\item Proxy blind signature scheme, Cryptology e-Print Archive, Report 2003/072 
              (2003) 
\item A scheme for obtaining a warrant message from digital proxy signatures 
               Cryptology e-Print Archive, Report 2003/073 (2003) 
\item Id-based ring signature and proxy ring signature schemes from bilinear 
               pairings Cryptology e-Print Archive, Report 2004/184 (2004) 
\item Security    analysis of a  dynamic ID-based remote user  authentication  scheme
               Cryptology e-Print Archive, Report 2004/238 (2004) 
\item A new remote user authentication scheme using smart cards with check digits. 
               \href{http://arxiv.org/abs/cs.CR/0504094}{[ArXiv]}
\item An Improved Remote User Authentication Scheme with Smart Cards using 
               Bilinear Pairings, Cryptology e-Print Archive, Report 2007/418, (2007)
\item  An  Improved  Timestamp Based  Password  Remote  User  Authentication  
               Scheme e-Print Archive, Report 2010/036 (2010)

\end{itemize}

\subsection*{Conference}

\begin{itemize}

\item Model for single level lot sizing and scheduling, IMS 64th annual conference, 
               Gurukul Kangri Univ. Haridwar 1998 
\item A note on password  authentication scheme based on unit circle, on analysis and    
             discrete structures, IITKharagpur 2002. International Conference*(Accepted) 
\item A delegated digital signature scheme, SCI 2003, Orlando, USA International    
       Conference*(Accepted)
\item Blind Signcryption, International Conference on number theory for secure 
               communications, SASTRA deemed university, Kumbakonam, Tamilnadu 2003 
\item Digital Signature Scheme (By S Mookerji) Gyanjyoti, HCST, Mathura 2003 
\item A new multi proxy signature scheme for partial delegation with warrant,  18th 
               RMS annual Conference., July 2003 
\item A delegated digital signature scheme with non-repudiation National conference 
               On application of mathematics in information technology, RBS College, Agra., 
               March 2003 
\item A new proxy ring signature scheme Proceeding of RMS Annual Conference 2004, 
               Page29. Also available at : 
							\href{http://arxiv.org/abs/cs.CR/0410010}{[ArXiv]}
\item An efficient scheme for sensitive message transmission using blind Signcryption, 
             10th annual conference of Vijnana Parishad of India, 2004, Bhopal, Also available 
              At: 
							\href{http://arxiv.org/abs/cs.CR/0504095}{[ArXiv]}
	\item  Gaurav Sharma, Shivam Gupta, Amit K. Awasthi and Garima Sharma, Use of Single Nucleotide Polymorphism in Disease Assessment and Management by using Geo-Informatics System, 4th International Conference on healthGIS 2011, 5-6 August, 2011, New Delhi, India
\end{itemize}

\subsection*{Proceedings}
\begin{itemize}
\item Awasthi, A. K. and Srivastava, K., A New User Authentication Scheme Using 
              Chaotic Hash Function on Mobile Devices, \emph{IEEE International Advance Computing 
               Conference (IACC 2009)}, Patiala, India, March, p. 1550-1553 (2009)
\item 	Arif Siddique, Amit K Awasthi, An Advance ATM Machine Service: Making Demand Draft through ATM Machine, 5th IEEE International Conference on Advanced Computing \& Communication Technologies [ICACCT-2011] , Ed. R.K. Choudhary, Manoj Verma and Sanjeev Saini, ABC Group of Publication, India November 05 (2011), pp. 10-14.
\end{itemize}

\section*{Other Research Activities}
\subsection*{Member of professional bodies }
\begin{itemize}
\item Indian Mathematical Society
\item Cryptology Research Society of India
\item Group for Cryptology Research
\item Group for Mathematics 
\item ACM  
\item ICST
\item European Alliance for Innovation
\item SDIWC Year:2011-12

\end{itemize}

\subsection*{Editor}
\begin{itemize}
\item Editor, Elsevier Science's Computer Standards \& Interfaces
\item Associate Editor, Elsevier Science's Computers \& Electrical Engineering 
\item Associate Editorial Board (IJCA) International Journal of Computer Applications 
\item Chief Editor - International Journal of Applied Mathematics and Computation 
\item International Journal of Network Security  
\item Asian Journal of Algebra as Technical Editor
\item Journal of Applied Sciences as Technical Editor
\item Research Journal of Information Technology as Technical Editor
\item Editorial Board in Special Issue on Applications and Security Services in Web and Pervasive Environments in Int. Journal of Intelligent Automation and Soft Computing
\end{itemize}

\subsection*{Reviewer}
\begin{itemize}
\item Elsevier Science's Journal of Systems and Software
\item Elsevier Science's Data \& Knowledge Engineering  
\item Elsevier Science's Computer Standards \& Interfaces
\item Elsevier Science's Computers \& Electrical Engineering
\item ACTA Press / IASTED - International Journal of Computers and Applications
\item IEEE Transactions on Consumer Electronics
\item IEEE Security \& Privacy
\item IEEE Transactions on Knowledge and Data Engineering
\item International Journal of Computer Mathematics
\item Journal of Computer Science and Technology (JCST)
\item Systematics Cybernetics and Informatics
\item International Journal of Network Security 
\item Journal of Computer Science and Technology 
\item International Journal of Computer Mathematics (worldscinet)
\item JAIT
\item JCP
\item IJoAT 
\item \textbf{Conferences}
	\begin{itemize}
	\item CCCT 2004 conference, CCCT 2010, CCCT 2011 conference
	\item IIS, Academia Sinica, JOURNAL OF INFORMATION SCIENCE AND ENGINEERING
	\item IMCIC 2010 conference
  \item ISAS 2010, 2011 conference, 
  \item AG 2010, 2011
  \item WMSCI 2010, 2011 Conference
  \item SICT 2010, 2011 Conference
  \item S2ES 2010, 2011 C0nference
	\end{itemize}
\end{itemize}

\subsection*{Program Committee}
\begin{itemize}
\item ICIEIS 2011 - MALAYSIA - University Technology Malaysia [SDIWC]
\item DEXA 2010 - SPAIN     -University of Deusto  [21st International Conference] 
\item NSSCT 2010 - KOREA    - Island Jeju   [International Conference]
\item DEXA 2009 - AUSTRIA -University of Linz  [20th International Conference]
\item National Conference on Techno-Lingual Communication - PSIT Kanpur (GBTU)
\item ICMR Sponsored Seminar on BIOSTATISTICS -  PSIT Kanpur (GBTU)
\item National Workshop on Polymer Science -  HCST Mathura (UPTU)
\end{itemize}

\section*{QIP/Workshop/Short term course}
\begin{itemize}
\item Faculty Development Program, IIT ROORKEE
\item Short Term Course on Environmental Impact Assessment, IIT KANPUR
\item Short Term Training Program on Quality Assurance in Technical Education, TTTI CHANDIGARH
\item Workshop on Methodology of Teaching Mathematics and Electrical Engineering at
       BBD Engineering College, LKO organized by UPTU
\item Faculty Development Program, HIMCS Mathura
\item A work shop on counseling skills at Agra, HIMCS Mathura 
\end{itemize}

\section*{Personal}

\begin{itemize}
\item S/o Sri Hari Om Awasthi
\item Born on August 06, 1977.
\item Permanant Address - Ghunghchai, Puranpur, Pilibhit, UP.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
